\section*{Introduction}
%\phantomsection

Whether you are an athlete, or you had an undergone surgery, or maybe you are just an usuall human being hoping to rid yourself of hand pain -- kinetotherapy is a great recovery strategy to help get read or heal off your injury. The goal of kinetotherapy is getting read of injures as much as possible and promote muscular function and mobility, to work the muscles and the area with an injury, to strengthen the muscles and joints so that they perform better.
Instead of depending on drug usage kinetotherapy recommends to rely on the body's ordinary resources of physical recovery through exercises.

Due to the expansions of medical-related technology new types of rehabilitation of patients are introduces. Here comes Kyno, a desktop application that helps users through rehabilitation by restoring movement and function of the hand which is affected by injury, illness or disability.

One of Kynos solutions, aims to treat patients with hand pain, tendons injuries and neuro disorders. With the help of a tracking device Kyno can manipulate the data and send the learning acitivy in the "virtual" environment, letting to patient's an open dor to focus more and pay attention to the details of their movements which might bring them closer to recovery.

Kyno is bringing a new wave of innovation and hope for patients everywhere. Among lots of benefits, it brings to the patients more fun while stretching and recovering their physical capacities. In my system the program with the help of Leap Motion device projects the patients hand onto a virtual environment shown on a screen. Then the patient by choosing one set of exercises will start performing it, which is aimed to improve their physical issue. While tradition kinetotherapy in most cases forces to use weights or other tools, kyno omits the usage of them. 

More then that traditional old kinetotherapy is forced to work in strict physical places, while using Kyno the patiens will not only strengthen their muscles or recover their injuries, but also will improve their cognitive abilities due to exploring a brand new borned application. He will have to understand how the application works and then how he should act in it. For instance, choosing what exercise to take involves decision taking(which on to choose), motor skill (moving the mouse over a button and then click it), attention (sustaining concentration on the virtual hand while performing the exercise it is a brain challenge). 

The program uses infrared light with a wavelength of 850 nanometers, which is outside the visible light spectrum
to track and analyze the movement of objects that are withing the range of the Leap Motion controller that connects the real world with the computer. During therapy the patients stays in front of the screen with the hand above the controller, where he can watch his own hands generated in the virtual world among some UI. The patient's work is to choose one type of exercise provided by the application, to read the instructions and start the process of rehabilitation. Modern technology works in a fraction of a second, so thanks to that the application is able to provide a realtime feedback that indicates if the exercises were done correctly or not. The application is designed with 3 exercises that are intended to improve the motor skills and neuro capability of the hand and fingers.

This thesis is composed of 4 chapters, a list of abbreviations, a list of figures, a table of contents, conclusion and reference. The report has roughly 70 pages. Starting with the first chapter where its been described the problem that needs to be solved, the solution that is purposed and the current market analysis.The second chapter describes the system architecture via UML diagrams and has a succint description of the UX. The third chapter is mostly about the technologies that are used and describes how the system is realized, with chunks of sample code listings.  The fourth chapter analyses the project from the point of economics view, where the expenses of building the project, the marketing plan and the profit it can make can be seen. 